\sysfull

### 2017-08-11 paper/evaluation.tex
table 4 needs fix

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{l|cc|cc|cc|cc|c}
		\hline
		{} & \multicolumn{2}{l|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for dd, dft, sort missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

>>>>

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{l|cc|cc|cc|cc|c}
		\hline
		{} & \multicolumn{2}{l|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & 180 & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand). DFT does not compile with Clang}
\label{table:compiler_result}
\end{table}
